What is an Ancestral Recombination Graph?

### 2022-03-03 paper.tex

@@

>>>>

[We should discuss the relationship between ARG nodes and SPRs
here. Cite \citep{deng2021distribution} too. Maybe we want to make
this a separate section, as it's a subtle and important point.]

@@

Espalier~\citep{rasmussen2022espalier} uses Maximum Agreement Forests to
minimise the differences between local trees estimated using other methods.
